cooking

### 2019-10-01 inst/cook.Rmd
more detail and rewriting

```{r cars}
library(hyper2)
H <- hyper2(pnames=letters[1:5])
H
```

@@

```{r}
H <- H +
    order_likelihood(c(5,2,3,4)) + # 1 cannot vote 
    order_likelihood(c(1,5,3,4)) + # 2 cannot vote
    order_likelihood(c(1,4,2,5)) + # 3 cannot vote
    order_likelihood(c(1,2,3,5)) + # 4 cannot vote
    order_likelihood(c(2,1,3,4))   # 5 cannot vote
H
```

graphically:

@@

>>>>

```{r cars}
library(hyper2)
H <- hyper2(pnames=paste("p",1:5,sep=""))
H
```

@@

```{r}
H <- H +
    order_likelihood(c(5,2,3,4)) + # person 1 says 5 is the best, 4 the worst.
    order_likelihood(c(1,5,3,4)) + # person 2 says 1 is the best, 4 the worst.
    order_likelihood(c(1,4,2,5)) + # person 3 says 1 is the best, 5 the worst.
    order_likelihood(c(1,2,3,5)) + # person 4 says 1 is the best, 5 the worst.
    order_likelihood(c(2,1,3,4))   # person 5 says 2 is the best, 4 the worst.
H
```

Note that noone is allowed to vote for themselves.  We may find
maximum likelihood estimate for the strengths,
$\operatorname{argmax}\mathcal{L}\left(p_1,\ldots,p_5\right)$
Graphically:

@@

We can assess the hypothesis that all players have the same strength:

```{r} 
L1 <- loglik(H,indep(equalp(H)))  # support at equal strengths
L2 <- loglik(H,indep(maxp(H)))    # maximum support
L2-L1
pchisq(2*(L2-L1),df=1,lower.tail=FALSE) # p-value of asymptotic distribution
```
